---
title: "R Notebook"
output:
  pdf_document:
    latex_engine: xelatex
  html_notebook: default
  html_document:
    df_print: paged
  word_document: default
---

# Running on Discovery

I recommend viewing this with a web-based Rstudio server on Discovery:

https://ood.discovery.neu.edu/pun/sys/dashboard/batch_connect/sys/RStudio/session_contexts/new

Press *Ctrl+Enter* to run a chunk.

# Initialization

*You may want to change the directories below.*

```{r setup}
suppressMessages(library(tidyverse))
library(stringr)
library(xtable)
suppressMessages(library(extrafont))
library(fontcm)
```

```{r dirs}
data_root <- "/proj/pinckney/experiments/aug-18-ripley-reproduce-results"

perf_root <- str_c(data_root, "-perf")
oldness_root <- str_c(data_root, "-oldness")
sizes_root <- str_c(data_root, "-sizes")


results_root <- str_c(data_root, "-number-results")
dir.create(results_root, showWarnings = FALSE)

tables_dir <- str_c(data_root, "-tables")
dir.create(tables_dir, showWarnings = FALSE)

plots_dir <- str_c(data_root, "-plots")
dir.create(plots_dir, showWarnings = FALSE)


results_tex <- str_c(results_root, "/results.tex")

write("% These are results from the R Notebook.", results_tex, append=FALSE)
write("% Run the notebook from top to bottom", results_tex, append=TRUE)
```


# Theme for output

```{r}
mytheme <- function() {
  return(theme_bw() +
           theme(
             # NOTE: UNCOMMENT WHEN RENDING PLOTS FOR THE PAPER
             # (can't get the CM fonts to work in artifact VM...)
             # text = element_text(family = "CM Roman", size=10),
              panel.grid.major = element_blank(),
             # panel.grid.minor = element_blank(),
             # panel.grid.major = element_line(colour="gray", size=0.1),
             # panel.grid.minor =
             #  element_line(colour="gray", size=0.1, linetype='dotted'),
             axis.ticks = element_line(size=0.05),
             axis.ticks.length=unit("-0.05", "in"),
             axis.text.y = element_text(margin = margin(r = 5)),
             axis.text.x = element_text(hjust=1),
             legend.key = element_rect(colour=NA),
             legend.spacing = unit(0.001, "in"),
             legend.key.size = unit(0.2, "in"),
             legend.title = element_blank(),
             legend.position = c(0.75, .7),
             legend.background = element_blank()))
}

mysave <- function(filename) {
  path <- str_c(plots_dir, "/", filename)
  ggsave(path, width=3, height=3, units=c("in"))
  # embed_font(path)
}

```

# Load the data

These are the results from running all experiments in parallel on Discovery.
The timing information is *not* reliable.
```{r}
raw_data <- read_csv(paste(data_root, "/results.csv", sep=""),
  col_types = cols(Status=col_factor(),
                   Project=col_factor(),
                   Rosette=col_logical(),
                   Consistency=col_factor(),
                   DisallowCycles=col_factor(),
                   Minimize=col_factor(),
                   Time=col_double(),
                   CVE=col_double(),
                   NDeps=col_integer()),
  show_col_types = FALSE)
                   
```

We load more data later.

# Manual Verification Step

Check that these are the factors that appear below:

1. *success*: everything worked!
2. *ERESOLVE*: depends on something that isn't in the repository
3. *ETARGET*: requires some other target architecture **verify**. Can also mean depending on something that doesn't exist.
4. *EBADPLATFORM*: requires some other platform (e.g., macOS)
5. *EUNSUPPORTEDPROTOCOL:* a dependency is in a format that NPM does not support
6. *unexpected*: something went wrong on Discovery. See experiment.out
7. *unavailable*: something went wrong and we didn't even capture the result. 
   See experiment.out
8. *unsat*: Z3 failed on us

```{r}
levels(raw_data$Status)
```

```{r}
levels(raw_data$Consistency)
```

```{r}
levels(raw_data$Minimize)
```

```{r}
levels(raw_data$DisallowCycles)
```

Sanity check: there should be 1,000 of each kind of experiment.

```{r}
num_experiments <- raw_data %>% 
  group_by(Rosette,AuditFix,Minimize,Consistency,DisallowCycles) %>%
  summarize(Count = n()) %>%
  ungroup() %>%
  select(Count) %>%
  unique()
stopifnot(nrow(num_experiments) == 1)
stopifnot(num_experiments[1] == 1000)
```


# CVE analysis

For each project, the CVE badness of dependencies with vanilla NPM, and with MinNPM
configured to minimize CVE and oldness, in that order.
```{r}
min_cve_analysis_tmp <-
  bind_rows(raw_data %>% 
            filter(Rosette == FALSE & AuditFix == "no" & Status == "success") %>% 
            select(Project,CVE) %>% 
            mutate(Solver="NPM_no"),
          raw_data %>% 
            filter(Rosette == FALSE & AuditFix == "yes" & Status == "success") %>%
            select(Project, CVE) %>%
            mutate(Solver="NPM_yes"),
          raw_data %>% 
            filter(Rosette == FALSE & AuditFix == "force" & Status == "success") %>%
            select(Project, CVE) %>%
            mutate(Solver="NPM_force"),
          raw_data %>% 
            filter(Rosette == TRUE & Status == "success" & Consistency == "npm" & DisallowCycles == "allow_cycles" &
                   Minimize == "min_cve,min_oldness") %>%
            select(Project, CVE) %>%
            mutate(Solver="NPM_MinCVE")) %>%
  pivot_wider(values_from=CVE, names_from=Solver) %>%
  filter(NPM_no>0) %>%

  mutate(NPM_no_NPM_yes_Delta = NPM_no - NPM_yes) %>%
  mutate(NPM_no_NPM_force_Delta = NPM_no - NPM_force) %>%
  
  mutate(NPM_no_MinCVE_Delta = NPM_no - NPM_MinCVE) %>%
  mutate(NPM_yes_MinCVE_Delta = NPM_yes - NPM_MinCVE) %>%
  mutate(NPM_force_MinCVE_Delta = NPM_force - NPM_MinCVE) %>%

  na.omit()

min_cve_analysis_tmp  

min_cve_analysis_delta <-
  min_cve_analysis_tmp %>%
  pivot_longer(cols = ends_with("Delta"), names_to="delta_comparison", values_to="Delta") %>%
  mutate(Comparison=delta_comparison) %>%
  select(Project,Comparison, Delta)

min_cve_analysis_delta
```

Comparison of cases:

Cases where `npm audit fix` does better than `npm install`:
```{r}
min_cve_analysis_delta %>% 
  filter(Comparison=='NPM_no_NPM_yes_Delta') %>%
  arrange(desc(Delta)) %>%
  filter(Delta > 0)
```

Cases where `npm audit fix --force` does better than `npm install`:
```{r}
min_cve_analysis_delta %>% 
  filter(Comparison=='NPM_no_NPM_force_Delta') %>%
  arrange(desc(Delta)) %>%
  filter(Delta > 0)
```

Cases where MinCVE does better than `npm install`:
```{r}
min_cve_analysis_delta %>% 
  filter(Comparison=='NPM_no_MinCVE_Delta') %>%
  arrange(desc(Delta)) %>%
  filter(Delta > 0)
```

Cases where MinCVE does better than `npm audit fix`:
```{r}
min_cve_analysis_delta %>% 
  filter(Comparison=='NPM_yes_MinCVE_Delta') %>%
  arrange(desc(Delta)) %>%
  filter(Delta > 0)
```

Cases where MinCVE does better than `npm audit --force`:
```{r}
min_cve_analysis_delta %>% 
  filter(Comparison=='NPM_force_MinCVE_Delta') %>%
  arrange(desc(Delta)) %>%
  filter(Delta > 0)
```

Cases where `npm audit --force` does better than MinCVE:
```{r}
min_cve_analysis_delta %>% 
  filter(Comparison=='NPM_force_MinCVE_Delta') %>%
  arrange(Delta) %>%
  filter(Delta < 0)
```


